Analytical Predictions of Explanet Obliquities Generated by Planet-Disk Interactions

### 2020-01-23 writeups/Su_disk_disp.tex
fix plots, plus footnote for DL first half review

To obtain the distribution of the final obliquities $\theta_{\rm f}$, we evenly
sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
value, we pick $101$ $\hat{s}$ initial conditions approximately on the ring
fixed by $\theta_{\rm sd, i}$%
%
\footnote{For each $\theta_{\rm sd, i}$ we choose an initial condition on the
libration cycle going through $\p{\theta_2 + \theta_{\rm sd, i}, \phi_2}$ (where
$\p{\theta_2, \phi_2}$ are the coordinates of CS2), such that all initial
conditions for a given $\theta_{\rm sd, i}$ enclose the same initial phase
space; see Section~\ref{sss:a_evo}.}.
%
To be concrete, we choose $\eta_{\rm i} = 10\eta_{\rm c}$ where $\eta_{\rm c}$
is given by Eq.~\eqref{eq:etac} and evolve Equations~\ref{eq:dsdt_base}
and~\ref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
small $\eta$, $\hat{s}$ is strongly coupled to $\hat{l}$ and the final obliquity
$\theta_{rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
$\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
20^\circ$ in Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
of the numerical calculation. The colored tracks are calculated
semi-analytically using the method discussed in the following subsection.

>>>>

To obtain the distribution of the final obliquities $\theta_{\rm f}$, we evenly
sample $101$ values of $\theta_{\rm sd, i}$, and for each $\theta_{\rm sd, i}$
value, we pick $101$ $\hat{s}$ approximately from the ring of initial conditions
having angular distance $\theta_{\rm sd, i}$ to $\hat{l}_{\rm d}$%
%
\footnote{
The procedure we adopted for choosing initial conditions is the natural
extension of this for finite $\eta_{\rm i}$. Note that the center of $\hat{s}$'s
libration is CS2, which, since $\eta_{\rm i}$ is finite, is different than
$\hat{l}_{\rm d}$. Furthermore, the libration is not exactly circular. Thus,
initial conditions on the circular ring of points having angular distance
$\theta_{\rm sd, i}$ from $\hat{l}_{\rm d}$ do not lie \emph{exactly} along each
others' trajectories, and will each enclose slightly different initial phase
space areas $A_{\rm i}$. Since our analytical theory assumes exact conservation
of phase space area $A_{\rm i}$ derived from $\theta_{\rm sd, i}$ (see
Section~\ref{ss:zone_transitions}), this discrepancy introduces an extra
deviation from the analytical prediction. To guarantee all points for a
particular $\theta_{\rm sd, i}$ have the same $A_{\rm i}$, we instead choose
initial conditions on the libration cycle going through $\p{\theta_2 +
\theta_{\rm sd, i}, \phi_2}$ (where $\p{\theta_2, \phi_2}$ are the coordinates
of CS2). This ensures that all initial conditions for a given $\theta_{\rm sd,
i}$ enclose the same initial $A_{\rm i}$. Note that as $\eta_{\rm i} \to
\infty$, CS2 becomes coincident with $\hat{l}_{\rm d}$ and the libration cycle
becomes exactly circular, recovering the procedure given in the text.}.
%
To be concrete, we choose $\eta_{\rm i} = 10\eta_{\rm c}$ where $\eta_{\rm c}$
is given by Eq.~\eqref{eq:etac} and evolve Equations~\ref{eq:dsdt_base}
and~\ref{eq:deta_dt} until $\eta$ reaches its final value $10^{-5}$. At such a
small $\eta$, $\hat{s}$ is strongly coupled to $\hat{l}$ and the final obliquity
$\theta_{rm f}$ is frozen. The mapping between $\theta_{\rm sd, i}$ and
$\theta_{\rm f}$ is our primary result, and is shown for $I = 5^\circ, 10^\circ,
20^\circ$ in Figs.~\ref{fig:ad_ensemble},~\ref{fig:3_ensemble_10_35},
and~\ref{fig:3_ensemble_20_35} respectively. The blue dots represent the results
of the numerical calculation. The colored tracks are calculated
semi-analytically using the method discussed in the following subsection.
